Fixing Vulnerabilities Potentially Hinders Maintainability

### 2021-02-01 response/response.tex

\begin{revcomment}[2.13]
    Section 3\\
    \begin{itemize}
        \item Page 10, line 49 "mainly single-commit patches" … "small percentage 
        of data points" - give us the exact numbers for each of these.  
        \item Page 11, line 38 - define "floss refactoring" and justify how these were objectively 
        and repeatably identified in your set. You say "these cases" which makes 
        it seems that you were including the set of patches that had more than one 
        commit as your (only) floss candidates.  
    \end{itemize}
\end{revcomment}

\Us Our dataset integrates $89.3\%$ of single-commit patches and 
$10.7\%$ of patches involving more than one commit. We replaced 
line 49 by the following one:

\begin{quote}
    Only $10.7\%$ of the data points 
of our dataset involve more than one commits, the other
$89.3\%$ of the cases are single-commit patches.
\end{quote}

We define floss-refactoring before in the paragraph
as you can see below. Regarding the methodology to detect floss-refactorings, 
we manually inspected all the cases to ensure that 
floss-refactorings were not being considered.

\begin{quote}
    The same approach is used to analyze the impact of regular 
    changes. Security patches can be performed through one commit (single-commit); 
    several consecutive commits (multi-commits); or, commit(s) interleaved with more 
    programming activities (floss-refactoring). Only $10.7\%$ of the data points 
    of our dataset involve more than one commit, the other
    $89.3\%$ of the cases are single-commit patches. We manually 
    inspected all the cases and identified $23$ floss-refactorings. 
    These were disregarded since it would not be fair to measure the 
    maintainability of these cases where other programming activities 
    are involved.
\end{quote}

### 2021-02-01 paper/emse20.tex
finished 2.13

The same approach is used to analyze the impact of regular 
changes. Security patches can be performed through one commit, 
several consecutive commits, or commit(s) interleaved with more 
programming activities (floss-refactoring). Only $10.7\%$ of the data points 
of our dataset involve more than one commits, the other
$89.3\%$ of the cases are single-commit patches. We manually 
inspected these cases and $23$ floss-refactorings were identified 
and disregarded since it would not be fair to measure the 
maintainability of these cases where other programming activities 
are involved.

>>>>

The same approach is used to analyze the impact of regular 
changes. Security patches can be performed through one commit (single-commit); 
several consecutive commits (multi-commits); or, commit(s) interleaved with more 
programming activities (floss-refactoring). Only $10.7\%$ of the data points 
of our dataset involve more than one commit, the other
$89.3\%$ of the cases are single-commit patches. We manually 
inspected all the cases and identified $23$ floss-refactorings. 
These were disregarded since it would not be fair to measure the 
maintainability of these cases where other programming activities 
are involved.
